---
title: "Homework_2"
author: "Linh Tran"
date: "9/24/2020"
output: github_document
---

```{r setup}
library(tidyverse)
library(readxl)
library(dplyr)
```

## Problem 1

Read the Mr. Trashwheel dataset.

```{r}
trashwheel_df = 
  read_xlsx("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
            sheet = "Mr. Trash Wheel",
            range = cell_cols("A:N")) %>% 
  janitor::clean_names() %>% 
  drop_na(dumpster) %>% 
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
```

Read precipitation data

```{r}
precip_2018 = 
  read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
             sheet = "2018 Precipitation",
             skip = 1
  ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2018) %>% 
  relocate(year)

precip_2017 = 
  read_excel("./data/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
             sheet = "2017 Precipitation",
             skip = 1
  ) %>% 
  janitor::clean_names() %>% 
  drop_na(month) %>% 
  mutate(year = 2017) %>% 
  relocate(year)
```

Now combine annual precipitation.

```{r}
month_df = 
  tibble(
    month= 1:12,
    month_name = month.name
  )
precip_df = 
  bind_rows(precip_2018, precip_2017) 

left_join(precip_df, month_df, by = "month")
```

This dataset contains information from the Mr.Trashwheel trash collector in Baltimore, Maryland. As trash enters the inner harbor, the trashwheel collects that trash, and stores it in a dumpster. The dataset contains information on year, month, and trash collected, include some specific kinds of trash. There are a total of `r nrow(trashwheel_df)` rows in our final dataset. Additional data sheets include month precpitation data. 

## Problem 2



```{r import and clean data}
#This code chunk is to read and clean the data

nyc_transit_df = read_csv("./data/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>% 
  janitor::clean_names() %>% 
  select(line, station_name, station_latitude, station_longitude, route1:route11, entry, vending, entrance_type, ada) %>% 
  mutate(entry = recode(entry, "YES" = TRUE, "NO" = FALSE)) %>% 
  mutate_at(vars(route8:route11), as.character)
```

This dataset contains `r names(nyc_transit_df)` variables. The dataset has dimensions of `r nrow(nyc_transit_df)` rows and `r ncol(nyc_transit_df)` columns. I imported the dataset, changed the variable names to snake cases, select the variables of interest and converted the entry variable from character to logical variable.


```{r reformat route number and route name}
#This code chunk reformats data so that route number and route name are distinct variables

nyc_transit_long = nyc_transit_df %>% 
  pivot_longer(route1:route11,
               names_to = "route_name",
               values_to = "route_number")
```

This dataset contains `r names(nyc_transit_df)` variables. The dataset has dimensions of `r nrow(nyc_transit_df)` rows and `r ncol(nyc_transit_df)` columns. I imported the dataset, changed the variable names to snake cases, select the variables of interest and converted the entry variable from character to logical variable. 



## Problem 3

